Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-11-26 README.qmd
Better badge for Zenodo

<!-- badges: start -->
[![Global Policy DOI](https://img.shields.io/badge/International%20Interactions%20DOI-10.1080%2F03050629.2024.2413965-brightgreen)](https://doi.org/10.1080/03050629.2024.2413965) [![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![International Interactions DOI](https://img.shields.io/badge/International%20Interactions-10.1080%2F03050629.2024.2413965-brightgreen)](https://doi.org/10.1080/03050629.2024.2413965)  
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.12817616-blue)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->
